Paper TITLE

### 2016-08-08 paper/Paper.Rmd
Sri's graphs side-by-side

```{r, echo = FALSE, fig.cap="Median Income Adjusted for the Number of People by Region"}
clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(aplmed, na.rm = T)) %>%
  mutate(region=as.character(region)) %>% 
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + 
  geom_line(size = 1) + 
  labs(x = "Year", y = "Median Adjusted Income (per persons)") + 
  scale_y_continuous(labels=function(x){paste0(x/1000, "K ")}) +
  scale_colour_brewer(palette = "Dark2", 
                      name = "Region", 
                      labels = regionNames) +
  theme_minimal(base_family = "serif")

>>>>

```{r, echo = FALSE, fig.cap="Median Income Adjusted for the Number of People by Region", fig.width=5, fig.height=5}
clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(aplmed, na.rm = T)) %>%
  mutate(region=as.character(region)) %>% 
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + 
  geom_line(size = 1) + 
  labs(x = "Year", y = "Median Adjusted Income (per persons)") + 
  scale_y_continuous(labels=function(x){paste0(x/1000, "K ")}) +
  scale_colour_brewer(palette = "Dark2", 
                      name = "Region", 
                      labels = regionNames) +
  theme_minimal(base_family = "serif")

clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(ablmed, na.rm = T)) %>%
  mutate(region = as.character(region)) %>% 
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + 
  geom_line(size = 1) +
  labs(x = "Year", y = "Median Adjusted Income (per persons)") +
  scale_y_continuous(labels=function(x){paste0(x/1000, "K ")}) +
  scale_colour_brewer(palette = "Dark2",
                      name = "Region", 
                      labels = regionNames) +
  theme_minimal(base_family = "serif")
